Software Citation Principles

### 2016-06-23 sc-principles/software-citation-principles.tex
adding VM words in 5.8 in response to a comment during the RFC period

The principles and discussion in this document have generally been written to focus on software
as source code.  However, we recognize that some software is only available as an executable or as a container, while other software may be available as a service.  We believe the principles apply to all of these forms of software, though the implementation of them will certainly differ based on software type.  When software exists as both source code and another type, we recommend that the source code be cited.

>>>>

The principles and discussion in this document have generally been written to focus on software
as source code.  However, we recognize that some software is only available as an executable, a container, or a virtual machine image, while other software may be available as a service.  We believe the principles apply to all of these forms of software, though the implementation of them will certainly differ based on software type.  When software exists as both source code and another type, we recommend that the source code be cited.
